Algorithmically Trading like a Human with GPT-J

### 2021-10-05 paper.tex
Experimented with TOC and LOF

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}

\section{Introduction}
Algorithmic trading has become the dominant way of buying and selling securities. In the U.S. stock market, algorithms account for 70-80\% of trading volume \cite{Samuelsson2021}. The next generation of trading algorithms use neural networks to improve prediction accuracy. However, current opinion states neural networks can only increase efficiency by about 10\% and that neural networks are not capable of inventing winning trading ideas \cite{Vonko2021}. We theorize that neural networks are capable of much more. By scaling the number of network parameters into the billions, training the network on a massive dataset which captures the complexities of human behavior, and then making inferences from current  and by feeding the network with current news and opinons we believe that neural networks can model the world accurately enough to discover winning, novel trade ideas. Thankfully, the creators of GPT-J have already created such a neural network \cite{mesh-transformer-jax}. GPT-J is a transformer network \cite{Vaswani2017} that has been trained on an 825GiB language modelling data set called The Pile \cite{Gao2021}. We propose that with adequate fine-tuning and well engineered prompts, GPT-J can learn to trade like a human by reading the news, social media, and other sources such as SEC filings.

@@

In summary, as algorihmic traders seek to employ increasingly competitive and complex trading algorithms, we intend to evaluate the viability of using GPT languange models to drive trading decisions. To achieve this goal we must first implement a trading algorithm based on GPT-J, then evaluate the accuracy of the algorithm's predictions, and finally evaluate the real-world profitability of the algorithm.

The contents of this paper are as follows: First we will explore competing algorithms and methods and how they compare with ours in section 2. Then we will describe our algorithm in section 3. Finally, we will evaluate our algorithm's accuracy and profitability using both backtesting and live market data in section 4.

>>>>

% \tableofcontents
% \listoffigures

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
The abstract goes here.
\end{abstract}
\section{Introduction}
Algorithmic trading has become the dominant way of buying and selling securities. In the U.S. stock market, algorithms account for 70-80\% of trading volume \cite{Samuelsson2021}. The next generation of trading algorithms use neural networks to improve prediction accuracy. However, current opinion states neural networks can only increase efficiency by about 10\% and that neural networks are not capable of inventing winning trading ideas \cite{Vonko2021}. We theorize that neural networks are capable of much more. By scaling the number of network parameters into the billions, training the network on a massive dataset which captures the complexities of human behavior, and then making inferences from current  and by feeding the network with current news and opinons we believe that neural networks can model the world accurately enough to discover winning, novel trade ideas. Thankfully, the creators of GPT-J have already created such a neural network \cite{mesh-transformer-jax}. GPT-J is a transformer network \cite{Vaswani2017} that has been trained on an 825GiB language modelling data set called The Pile \cite{Gao2021}. We propose that with adequate fine-tuning and well engineered prompts, GPT-J can learn to trade like a human by reading the news, social media, and other sources such as SEC filings.

@@

\subsection{Problem Statement}
In summary, as algorihmic traders seek to employ increasingly competitive and complex trading algorithms, we intend to evaluate the viability of using GPT languange models to drive trading decisions. To achieve this goal we must first implement a trading algorithm based on GPT-J, then evaluate the accuracy of the algorithm's predictions, and finally evaluate the real-world profitability of the algorithm.
